---
title: "2_Recreate"
author: "Caleb Kornfein"
date: "3/17/2022"
output: pdf_document
---

### Load Packages

```{r setup, include=FALSE}
library(tidyverse)
library(ggthemes)
library(lemon)
library(kableExtra)
df <- read.csv("GFR2.csv")
df$Statins <- factor(df$Statins, labels = c("No", "Yes"))
```


### Recreate Figure

```{r model}
fig_model <- lm(GMR.Post ~ GMR.Pre + Statins, data=df)
fig_model_summary <- as.data.frame(coef(summary(fig_model)))

kable(fig_model_summary)

slope = fig_model_summary$Estimate[2]
intercept = fig_model_summary$Estimate[1] + fig_model_summary$Estimate[3]
```

```{r model, fig.height=5, fig.width=5, fig.align="center"}
ggplot(df, aes(x=GMR.Pre, y=GMR.Post, color=Statins, shape=Statins), size = 10) +
      geom_point() +
      labs(y= "Maximum post-surgery", 
           x = "Pre-surgery",
           title = "Glomerular filtration rate") +
      scale_color_manual(name = "Statin use",
                         labels= c('No', 'Yes'),
                         values=c('chartreuse4','royalblue3')) +
      scale_shape_manual(name = "Statin use",
                         labels= c('No', 'Yes'),
                         values = c(1,  16)) +
      scale_y_continuous(breaks = c(0, 25, 50, 75, 100, 125, 150, 175),
                         limits = c(0,175)) +
      scale_x_continuous(breaks = c(0, 25, 50, 75, 100, 125, 150, 175),
                         limits = c(0,175)) + 
      geom_abline(intercept = intercept, slope = slope, color = "deeppink4", size = 0.4, alpha = 0.8) +
      theme(plot.title = element_text(hjust = 0.5, size = 10), 
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line.x = element_line(colour = "black", size=0.4),
            axis.line.y = element_line(colour = "black", size=0.4),
            panel.background = element_blank(),
            legend.background = element_rect(fill = "white", colour = "black"),
            legend.position = c(0.23, 0.7),
            legend.key=element_blank(),
            legend.margin = margin(-0.6, -0.15, 0, 0, unit = "cm"),
            text = element_text(size = 12),
            axis.ticks.length = unit(0.3, "cm"),
            axis.text = element_text(size = 10),
            plot.margin = margin(15, 15, 15, 15),
            axis.text.x = element_text(colour="black", size = 10),
            axis.text.y = element_text(colour="black", size = 10),
            legend.text = element_text(colour="black", size = 10)) +
      coord_capped_cart(bottom="both", left="both")


ggsave(file="figure1.png", width=5, height=5, dpi=600)
```
### Recreate Table

```{r}
table_model <- lm(GMR.Post ~ 
                  GMR.Pre + 
                  Age + 
                  Weight + 
                  Female + 
                  Diabetes + 
                  CHF + 
                  Pulm + 
                  Renal.Insuff +
                  Acetylcystine + 
                  Emergency + 
                  HCT.Intraop +
                  TVol +
                  Crystalloid +
                  Colloid +
                  Statins, data=df)
table_model_summary <- as.data.frame(coef(summary(table_model)))

kable(table_model_summary)
```
First let's calculate the confidence interval and then scale the intervals and coefficient estimates using the "adjusted" proportions from the table.

```{r}
# generate 95% confidence intervals
intervals <- confint(table_model)
colnames(intervals) <- c("lower", "upper")
intervals <- as.data.frame(intervals)

table_model_summary$lower <- intervals$lower
table_model_summary$upper <- intervals$upper

# adjust for proportions
adjust <- function(variable, factor, df){
  for (string in c("Estimate", "lower", "upper")){
    df[variable, string] <- factor * df[variable, string]
  }
  return(df)
}

table_model_summary <- adjust("GMR.Pre", 20, table_model_summary)
table_model_summary <- adjust("Age", 5, table_model_summary)
table_model_summary <- adjust("Weight", 10, table_model_summary)
table_model_summary <- adjust("HCT.Intraop", 5, table_model_summary)
table_model_summary <- adjust("TVol", 100, table_model_summary)
table_model_summary <- adjust("Crystalloid", 1000, table_model_summary)
table_model_summary <- adjust("Colloid", 500, table_model_summary)
```

Now that we have derived all the Adjusted estimates and their confidence intervals, lets create the variables to output in the final data frame.

```{r}
# create the output CI variable
table_model_summary <- table_model_summary %>%
  mutate(outCI = paste(round(Estimate, digits=0), " (", round(lower, digits=0), ", ", round(upper, digits=0), ")", sep=""))

# only keep the rows to be displayed
table_model_summary <- table_model_summary[2:16, ]
table_model_summary <- table_model_summary[c("outCI", "Pr(>|t|)")]

# add in row and column names
rownames(table_model_summary) <- c("Preoperative eGFR (increase of 20 ml min\\textsuperscript{-1} 1.73 m\\textsuperscript{-2})", "Patient age (increase of 5 yr)", "Weight (increase of 10 kg)", "Female gender (vs male)", "Diabetes (vs none)", "History of CHF (vs none)", "History of pulmonary disease (vs none)", "History of chronic kidney disease (vs none)", "Use of acetylcysteine (vs none)", "Emergent case (vs scheduled)", "Intraoperative haematocrit (increase of 0.05)", "Total volume (increase of 0.1 litre kg\\textsupercript{-1} h\\textsuperscript{-2})", "Crystalloids (increase of 1 litre)", "Colloids (increase of 0.5 litre)", "Statin use (vs none)")

super <- c("Preoperative eGFR (increase of 20 ml min\\textsuperscript{-1} 1.73 m\\textsuperscript{-2})", "Patient age (increase of 5 yr)", "Weight (increase of 10 kg)", "Female gender (vs male)", "Diabetes (vs none)", "History of CHF (vs none)", "History of pulmonary disease (vs none)", "History of chronic kidney disease (vs none)", "Use of acetylcysteine (vs none)", "Emergent case (vs scheduled)", "Intraoperative haematocrit (increase of 0.05)", "Total volume (increase of 0.1 litre kg\\textsupercript{-1} h\\textsuperscript{-2})", "Crystalloids (increase of 1 litre)", "Colloids (increase of 0.5 litre)", "Statin use (vs none)")

super2 <- c("Preoperative eGFR (increase of 20 ml min^-1^ 1.73 m^-2^)", "Patient age (increase of 5 yr)", "Weight (increase of 10 kg)", "Female gender (vs male)", "Diabetes (vs none)", "History of CHF (vs none)", "History of pulmonary disease (vs none)", "History of chronic kidney disease (vs none)", "Use of acetylcysteine (vs none)", "Emergent case (vs scheduled)", "Intraoperative haematocrit (increase of 0.05)", "Total volume (increase of 0.1 litre kg^-1^ h^-2^)", "Crystalloids (increase of 1 litre)", "Colloids (increase of 0.5 litre)", "Statin use (vs none)")

table_model_summary <- table_model_summary %>% mutate(rows = rownames(table_model_summary))

table_model_summary <- table_model_summary[c("rows", "outCI", "Pr(>|t|)")]

colnames(table_model_summary) <- c("Effect", "Adjusted* difference (95% CI) in mean postoperative eGFR","Pvalue")
```

```{r}
# create the formatted P-value column
table_model_summary <- table_model_summary %>%
  mutate(Pvalue = case_when(Pvalue < 0.001 ~ "<0.001",
                             Pvalue < 0.01 ~ paste(format(round(Pvalue, digits=3), nsmall=3), sep=""),
                             Pvalue < 1 ~ paste(format(round(Pvalue, digits=2), nsmall=2), sep="")))
```

Now let's make the table look nice! Note, much help with creating nice tables was taken from the code in: https://towardsdatascience.com/create-latex-and-ms-word-tables-in-r-6ac919204247.

```{r}
table_model_summary$Effect <- super2

table_model_summary %>%
  kbl(caption = "Reproduction of Table 2",
      format="html",
      align="c",
      row.names = FALSE,
      col.names = c("Effect", "Adjusted* difference (95% CI) in mean postoperative eGFR","P-value"),
      escape = FALSE) %>%
  kable_classic(full_width = F, html_font = "Helvetica")
```

